Recovering from population extinction in the Animal Life Cycle Algorithm (ALCA)

### 2022-09-30 paper.tex
Updated Paper
Work in progress.

    The main contribution of this paper is to demonstrate that it is possible to
    evolve a population of individuals, similar to a Genetic Algorithm (GA), using
    a distributed, parallel, and asynchronous methodology by algorithm
    implementation and testing.
    % The main contribution is not this, is the restarting method? - M 
    We improve the algorithm behavior by solving
    population extinction caused by nature's pressure in the Animal Life Cycle % This is more a contribution - M
    Algorithm with one of the most promising alternatives: the projection of the
    Elite towards the Champion, where we compare the results obtained with the
    latter and the random use of the more traditional alternatives (mutation and
    crossover), using classic benchmark functions for optimization for comparison.

    We present the description of the following sections in our paper. First, we % This paper is organized as follows - M

    illustrate our algorithm model, the encountered problem with the occasional
    population extinction, and our proposed solution in
    section~\ref{section.proposal}, followed by our experimental configuration and
    results in section~\ref{section.experiments}, where we continue to analyze and
    describe some of our research findings in section~\ref{section.discussion}. We
    finalize by presenting some inferences based on the results of our experiments
    in section~\ref{section.conclusions}.

@@

    In previous work, we presented an algorithm inspired by nature, where we % Reference
    % used observation, analysis, and abstraction to 
    model our algorithm based on
    the generalization of the life cycle of animal species. Our algorithm, as
    in nature, consists of four stages \cite{read1968system}: birth, growth,
    reproduction, and death. One key concept of our idea is that combining
    those processes evolves the population. We propose to execute all these
    stages in parallel and asynchronously on a continuously evolving
    population.

@@

         % \subsubsection{How does it work?}

>>>>

    One contribution of this paper is to demonstrate that it is possible to
    evolve a population of individuals, similar to a Genetic Algorithm (GA),
    using a distributed, parallel, and asynchronous methodology by algorithm
    implementation and testing.

    The main contribution of this research is to demonstrate how to improve the
    algorithm's behavior, by solving population extinction caused by nature's
    pressure in the Animal Life Cycle Algorithm with one of the most promising
    alternatives: the projection of the Elite towards the Champion. To validate
    our findings, we compare the results obtained with the latter and the
    random use of the more traditional alternatives (mutation and crossover),
    using classic benchmark functions for optimization for comparison.

    This paper is organized as follows. First, we 
    illustrate our algorithm model, the encountered problem with the occasional
    population extinction, and our proposed solution in
    section~\ref{section.proposal}, followed by our experimental configuration and
    results in section~\ref{section.experiments}, where we continue to analyze and
    describe some of our research findings in section~\ref{section.discussion}. We
    finalize by presenting some inferences based on the results of our experiments
    in section~\ref{section.conclusions}.

@@

    In previous work, we presented an algorithm inspired by nature, where we % Reference
    model our algorithm based on
    the generalization of the life cycle of animal species. Our algorithm, as
    in nature, consists of four stages \cite{read1968system}: birth, growth,
    reproduction, and death. One key concept of our idea is that combining
    those processes evolves the population. We propose to execute all these
    stages in parallel and asynchronously on a continuously evolving
    population.

@@
